### 2021-08-27 notes.tex
Updates from Overleaf

Let $X_i^* \sim Binomial(n_i, \theta_i^*)$ for $i=1,\ldots,k$. We are interested in the prevalence of disease in the population. Suppose there are $N_i$ individuals in the population of unit $i$. Then the prevalence of the population is
\begin{eqnarray*}
\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i,
\end{eqnarray*}
where $w_i = N_i/N$ and $N=\sum_{j=1}^{k} N_j$.

@@

@@

\subsection{Results for varying Coeficient of Variation, Number of Weights with Non-Zero Prevalence, and Distribution of Weights with Non-Zero Prevalence}

@@

Results are presented on the next two pages.
\todo[inline]{Would like to make these figures smaller / more focused. Maybe we don't need to present all of the ``Weights with Non-0 Prevalence."}
\todo[inline]{Maybe need to simulate prevalence \( > 0.005 \) to show wsPoisson failing}
\begin{itemize}
    \item Regardless of the scenario, the two wsPoisson methods achieve at least the desired coverage. This coverage increases as the coefficient of variation among the weights increases.
    \item Regardless of the scenario, when the coefficient of variation among the weights is near 0, all methods perform well.
    \item Regardless of the scenario, when the prevalence is concentrated among the largest weights, increasing coefficient of variation among the weights results in lower coverage for the Agresti-Coull and Clopper-Pearson methods. 
    \item Regardless of the scenario, when the prevalence is concentrated among the smallest weights, increasing coefficient of variation among the weights results in higher coverage for all methods.
    \item When the prevalence is distributed uniformly among the weights, Scenario 1 exhibits similar behavior to when the prevalence is concentrated among the smallest weights.
    \items When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.

\end{itemize}

@@

>>>>

Let $X_i^* \sim Binomial(n_i, \theta_i^*)$ for $i=1,\ldots,k$. We are interested in the prevalence of disease in the population. Suppose there are $N_i$ individuals in the population of unit $i$. Then the prevalence of the population is
\begin{eqnarray*}
\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i^*,
\end{eqnarray*}
where $w_i = N_i/N$ and $N=\sum_{j=1}^{k} N_j$.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Combined_comparison_plots.pdf}
    \caption{Caption}
    \label{fig:Combined_comparison_plots}
\end{figure}

@@

\subsection{Results for varying Coefficient of Variation, Number of Weights with Non-Zero Prevalence, and Distribution of Weights with Non-Zero Prevalence}

@@

Results are presented on the next two pages.
\todo[inline]{Would like to make these figures smaller / more focused. Maybe we don't need to present all of the ``Weights with Non-0 Prevalence."}
\todo[inline]{Maybe need to simulate prevalence \( > 0.005 \) to show wsPoisson failing}
\begin{itemize}
    \item Regardless of the scenario, the two wsPoisson methods achieve at least the desired coverage. This coverage increases as the coefficient of variation among the weights increases.
    \item Regardless of the scenario, when the coefficient of variation among the weights is near 0, all methods perform well.
    \item Regardless of the scenario, when the prevalence is concentrated among the largest weights, increasing coefficient of variation among the weights results in lower coverage for the Agresti-Coull and Clopper-Pearson methods. 
    \item Regardless of the scenario, when the prevalence is concentrated among the smallest weights, increasing coefficient of variation among the weights results in higher coverage for all methods.
    \item When the prevalence is distributed uniformly among the weights, Scenario 1 exhibits similar behavior to when the prevalence is concentrated among the smallest weights.
    \item When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.
\end{itemize}

@@

\begin{landscape}
\includepdf[angle=90]{upper_error_frequency_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{upper_error_frequency_8000}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{lower_error_frequency_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{lower_error_frequency_8000}
\end{landscape}
